### 2015-09-09 results.tex
Fixing filter table
Cleaning up.

\subsection{Cartesian Lattice}
\subsubsection{Basis function}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$. Due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{C4}}$.

@@

\subsection{BCC Lattice}
\subsubsection{Basis function}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}

generates a piecewise linear polynomial function \cite{practicalbox}. The support of this box spline is a rhombic dodecahedron, which incidentally contains the set of first nearest neighbors to the Voronoi region of the lattice at the origin, and is a natural fit for the lattice. The quintic box spline is given by the matrix $\mathbf{\Xii_{B2}} := \left[\mathbf{\Xii_{B}} \ \mathbf{\Xii_{B}}\right]$, or may also be seen as the convolution of the linear box spline with itself.  However, there exist both an efficient piecewise polynomial representation \cite{practicalbox}, and an efficient implementation \cite{fastbox} of these piecewise quintic polynomial functions. Again, due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{B2}}$.

@@

The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree
$k$. The filters used in our experiments are tabulated in
Table~\ref{tab:filters}.

@@

\begin{table}[!t]
	%% increase table row spacing, adjust to taste
	\renewcommand{\arraystretch}{1.5}
	% if using array.sty, it might be a good idea to tweak the value of
	%\extrarowheight % as needed to properly center the text within the cells
	\centering
	% Some packages, such as MDW tools, offer better commands for making tables
	% than the plain LaTeX2e tabular which is used here.
	\begin{tabular}{|r||c||c|c|}
		\hline
		Filter & Notation & Filter wieghts  \\
		\hline
		\hline
		Derivative & $d[n]$ & $[\frac{-1}{12} \ \frac{2}{3} \ 0 \ \frac{-2}{3} \ \frac{1}{12}]$ \\
		\hline
		Shifted Derivative & $s[n]$  & $[\frac{-1}{24} \ \frac{9}{8} \ \frac{-9}{8} \ \frac{1}{24} \ 0]$ \\
		\hline
		Second Derivative & $l[n]$  & $[\frac{-1}{12} \ \frac{4}{3} \ \frac{-5}{2} \ \frac{4}{3} \ \frac{-1}{12}]$ \\
		\hline
	\end{tabular}
	\caption{Filters used in our experiments. These filters are applied along the principal lattice directions.}
	\label{tab:filters}
\end{table}

@@

Quantitatively, we evaluate whether function spaces on the BCC lattice provide better approximation spaces than those on the Cartesian lattice. In order to reduce any artifacts that may arise from any noise or the non-uniformity of the data, we utilize the ideal reference point-sets of our test models.  We measure both the Hausdorff distance, mean distance, and angle deviation from the original shape with the tools provided by Berger et al.~\cite{reconbench}. We evaluate the FFT, Poisson, and Screened Poisson surface reconstruction algorithms, as their theory is close to ours. We choose $\lambda_1$ and $\lambda_2$ so that the reconstructions are comparable to the Screened Poisson results.

@@

%You should really try to bring out the role of the shifts.
We fix the resolution of the grid at $128^3$, and reconstruct the remaining models (\FG{fig:t2}.) We choose this resolution as it seems to be a point of contention between the cases with the Gargoyle model. However, there seems to be a consistent advantage in using the BCC lattice over the Cartesian lattice. Moreover, in both cases, we noticed that introducing a shift tends to reduce all error metrics. Unfortunately, reconstructing the divergence of the smoothed vector field from more than three lattice directions produced little difference. \FG{fig:r1} shows a visual comparison of the techniques. We manage to outperform the FFT and Poisson techniques by a large margin, and outperform the screened Poisson case.

>>>>

\subsection{Cartesian Lattice}
\subsubsection{Basis function}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a tri-linear piecewise polynomial. 
By definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. 
Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$. 
A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. 
We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$. 
Due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{C4}}$.

@@

\subsection{BCC Lattice}
\subsubsection{Basis function}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}
generates a piecewise linear polynomial function \cite{practicalbox}. 
The support of this box spline is a rhombic dodecahedron, which incidentally contains the set of first nearest neighbors to the Voronoi region of the lattice at the origin, and is a natural fit for the lattice. 
The quintic box spline is given by the matrix $\mathbf{\Xii_{B2}} := \left[\mathbf{\Xii_{B}} \ \mathbf{\Xii_{B}}\right]$, or may also be seen as the convolution of the linear box spline with itself. 
However, there exist both an efficient piecewise polynomial representation \cite{practicalbox}, and an efficient implementation \cite{fastbox} of these piecewise quintic polynomial functions. 
Again, due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{B2}}$.

@@

The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree $k$. 
The filters used in our experiments are tabulated in table~\ref{tab:filters}.

@@

\begin{table}[!t]
	%% increase table row spacing, adjust to taste
	\renewcommand{\arraystretch}{1.5}
	% if using array.sty, it might be a good idea to tweak the value of
	%\extrarowheight % as needed to properly center the text within the cells
	\centering
	% Some packages, such as MDW tools, offer better commands for making tables
	% than the plain LaTeX2e tabular which is used here.
	\begin{tabular}{|r||c||c|c|}
		\hline
		Filter & Notation & Filter wieghts  \\
		\hline
		\hline
		Derivative & $d[n]$ & $[\frac{-1}{12} \ \frac{2}{3} \ 0 \ \frac{-2}{3} \ \frac{1}{12}]$ \\
		\hline
		Shifted Derivative & $s[n]$  & $[\frac{-1}{24} \ \frac{9}{8} \ \frac{-9}{8} \ \frac{1}{24} \ 0]$ \\
		\hline
		Second Derivative & $l[n]$  & $[\frac{-1}{12} \ \frac{4}{3} \ \frac{-5}{2} \ \frac{4}{3} \ \frac{-1}{12}]$ \\
		\hline
	\end{tabular}
	\caption{Filters used in our experiments. These filters are applied along the principal lattice directions.}
	\label{tab:d_filters}
\end{table}

@@

Quantitatively, we evaluate whether function spaces on the BCC lattice provide better approximation spaces than those on the Cartesian lattice. In order to reduce any artifacts that may arise from any noise or the non-uniformity of the data, we utilize the ideal reference point-sets of our test models.  
We measure both the Hausdorff distance, mean distance, and angle deviation from the original shape with the tools provided by Berger et al.~\cite{reconbench}. 
We evaluate the FFT, Poisson, and Screened Poisson surface reconstruction algorithms, as their collective underlying theory and methodology is close to ours. 
We choose $\lambda_1$ and $\lambda_2$ so that the reconstructions are comparable to the Screened Poisson results.

@@

%You should really try to bring out the role of the shifts.
We fix the resolution of the grid at $128^3$, and reconstruct the remaining models (\FG{fig:t2}), 
We choose this resolution as it seems to be a point of contention between the cases with the Gargoyle model.
However, there seems to be a consistent advantage in using the BCC lattice over the Cartesian lattice. 
Moreover, in both cases, we noticed that introducing a shift tends to reduce all error metrics. 
Unfortunately, reconstructing the divergence of the smoothed vector field from more than three lattice directions produced little difference. 
\FG{fig:r1} shows a visual comparison of the techniques. 
We manage to outperform the FFT and Poisson techniques by a large margin, and outperform the screened Poisson case.
